\section{Results}

\subsection{Current empirical status}

No participant-level dataset is currently archived in this repository snapshot. As of March 13, 2026, the paper package does not include a sample description, trial counts, condition assignments, press-event logs, questionnaire exports, physiological recordings, exclusion decisions, or inferential analysis outputs. For that reason, no empirical effect sizes, descriptive statistics, significance tests, or qualitative themes are reported here. The absence is documented explicitly in \texttt{DATA\_GAPS.md} so that a later collaborator can replace this scaffold with real results rather than infer what went missing from the prose.

\subsection{Truthful results scaffold}

When the dataset becomes available, the results section should be rewritten around the following families of findings.

\begin{table}[t]
\centering
\begin{tabular}{|p{3.3cm}|p{4.6cm}|p{5.2cm}|}
\hline
\textbf{Outcome family} & \textbf{Expected input} & \textbf{Current status} \\
\hline
Pressing behavior & press count, time to first press, abstention rate, inter-press intervals & no event log archived \\
\hline
Condition effects & live ECG versus sham ECG comparisons, order terms, interaction terms & no condition table or model output archived \\
\hline
Subjective reports & presence, peripersonal space, oneness, secondness & no questionnaire export archived \\
\hline
Physiological coupling & heart-rate timing, breathing-linked lighting summaries, manipulation checks & no raw signal files archived \\
\hline
Temporal complexity & entropy, recurrence, burst, scaling, branching metrics & no analysis scripts or derived outputs archived \\
\hline
\end{tabular}
\caption{Result families specified by the current protocol, alongside the repository materials still needed to report them truthfully.}
\end{table}

\subsection{What a completed results section should answer}

Once data are available, the core empirical questions are straightforward.

\begin{enumerate}
\item Do participants press the button at all, and how variable is voluntary pressing under explicit permission to abstain?
\item Does live physiological coupling change press count, time to first press, or subjective proximity relative to sham coupling?
\item Are order and novelty effects larger than condition effects?
\item Do presence, peripersonal space, oneness, and secondness move together, or do they diverge?
\item Does the temporal structure of pressing show bursts, regularization, or other patterned dynamics rather than simple accumulation?
\end{enumerate}

Until those questions can be answered with archived evidence, the correct result is restraint.
